Manuscript draft

### 2019-09-10 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

>>>>

### Supporting Information

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/S1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, booktabs = TRUE, caption = "Hypothesis table", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"))
```
